---
title: "18a: Shiny Layouts"
author: |
  | Jerzy Wieczorek
  | Department of Mathematics & Statistics
  | Colby College
date: "5/3/21"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
runtime: shiny
---

This is a continuation of `Lecture18_ShinyAndPlotly.Rmd`, with more specific details: common issues working Shiny, changing the layout or theme, etc.

Note: today's lecture demonstrates interactive graphs with Shiny, so I cannot knit it as a standalone HTML file. You have to open this Rmd file in RStudio and run it there, so that the Shiny demos are connected to a running instance of R.

***



# Layouts in Shiny

## Basic layout

We recreate the dataset from the main lecture:

```{r warning=FALSE, message=FALSE}
library(tidyverse)
state_df <- cbind(State = row.names(state.x77), Region = state.region,
                  data.frame(state.x77))
```


Here is a Shiny example from the main lecture. Our `ui` object has an `inputPanel` on top, then a single `plotOutput` below.

```{r lecture18, warning=FALSE, message=FALSE}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      
      sliderInput("point_size", label = "Point size:",
                  min = 0.5, max = 3, value = 2, step = 0.5),

      checkboxInput("show_conf", label = "Include confidence band")
  
    ),
    
    plotOutput("state_plot")
  ),
  
  server = function(input, output) {
    output$state_plot <- renderPlot({
      
      ggplot(state_df, aes(x = HS.Grad, y = Illiteracy)) +
        geom_point(size = input$point_size) + 
        geom_smooth(method = "lm", se = input$show_conf) +
        labs(x = "HS Graduation Rate",
             title = "Education vs Illiteracy in US States in 1977")
      
    })
  },
  
  options = list(height = 550)
)
```

## Sidebar Layout

Using ideas from RStudio's [Shiny Lesson 2, "Build a user interface,"](https://shiny.rstudio.com/tutorial/written-tutorial/lesson2/) we can make a slightly cleaner design for our interactive app. Let us use a `sidebarLayout` which will put all of the input widgets in a `sidebarPanel` on the left, then show our outputs in a `mainPanel` on the right. Let's also add a text paragraph with `p()` to describe our data source inside the `sidebarPanel`.

Finally, we can also add a `titlePanel` on the top, outside the `sidebarLayout`.

Nothing changes in the `server` code.

```{r layout, warning=FALSE, message=FALSE}
shinyApp(
  
  ui = fluidPage(
    titlePanel("Lecture 18a Layout Example"),
    
    sidebarLayout(
      sidebarPanel(
      
        sliderInput("point_size", label = "Point size:",
                    min = 0.5, max = 3, value = 2, step = 0.5),
  
        checkboxInput("show_conf", label = "Include confidence band"),
        
        p("Data source: state.x77 data from R's datasets package.")
    
      ),
      
      mainPanel(
        plotOutput("state_plot")
      )

    )
  ),
  
  server = function(input, output) {
    output$state_plot <- renderPlot({
      
      ggplot(state_df, aes(x = HS.Grad, y = Illiteracy)) +
        geom_point(size = input$point_size) + 
        geom_smooth(method = "lm", se = input$show_conf) +
        labs(x = "HS Graduation Rate",
             title = "Education vs Illiteracy in US States in 1977")
      
    })
  },
  
  options = list(height = 550)
)
```

## More Outputs

Finally, recreate the app above, but add another output. This time, include a `textOutput` telling viewers whether a confidence band was selected. We need to add a `renderText` in the `server` object to do this.


```{r outputs, warning=FALSE, message=FALSE}
shinyApp(
  
  ui = fluidPage(
    titlePanel("Lecture 18a Layout Example"),
    
    sidebarLayout(
      sidebarPanel(
      
        sliderInput("point_size", label = "Point size:",
                    min = 0.5, max = 3, value = 2, step = 0.5),
  
        checkboxInput("show_conf", label = "Include confidence band"),
        
        p("Data source: state.x77 data from R's datasets package.")
    
      ),
      
      mainPanel(
        textOutput("is_conf_shown"), 
        plotOutput("state_plot")
      )

    )
  ),
  
  server = function(input, output) {
    output$state_plot <- renderPlot({
      
      ggplot(state_df, aes(x = HS.Grad, y = Illiteracy)) +
        geom_point(size = input$point_size) + 
        geom_smooth(method = "lm", se = input$show_conf) +
        labs(x = "HS Graduation Rate",
             title = "Education vs Illiteracy in US States in 1977")
      
    })
    
    output$is_conf_shown <- renderText({
      if(input$show_conf) {
        return("Regression line with 95% confidence band:")
      } else {
        return("Regression line (no confidence band):")
      }
    })
  },
  
  options = list(height = 550)
)
```

## More on Layouts in Shiny

Read the [Layout Guide](https://shiny.rstudio.com/articles/layout-guide.html) for other options such as grid layouts, tabsets, navlists, etc.

You can use these approaches to create a fully-customized layout for your Shiny app, with fine control over the location of each component.

On the other hand, sometimes you will prefer to follow a professional-looking template that someone else has made. We will see examples in the next section.

***

# Dashboards with Shiny

Here are two ways to make clean, professional-looking layouts with Shiny.

## `shinydashboard` vs `flexdashboard`

Flex Dashboard (`flexdashboard`) is a really nice way to integrate your RMarkdown knowledge with Shiny.  It creates great-looking dashboard-style output that can be used when creating interactive graphics. And it can be used with other kinds of interaction, not just Shiny:

+  [https://blog.rstudio.org/2016/05/17/flexdashboard-easy-interactive-dashboards-for-r/]
+  [http://rmarkdown.rstudio.com/flexdashboard/]
+  [http://rmarkdown.rstudio.com/flexdashboard/examples.html]
+  [https://cran.r-project.org/web/packages/flexdashboard/index.html]

On the other hand, another framework called `shinydashboard` is specifically designed to work well with Shiny. This has several Shiny widgets designed particularly for dashboard layouts.

+ [https://rstudio.github.io/shinydashboard/]
+ [https://rstudio.github.io/shinydashboard/examples.html]
+ [https://cran.r-project.org/web/packages/shinydashboard/index.html]

`shinydashboard` **must** be connected to a running R instance, either on your local computer or online such as with ShinyApps.io. However, `flexdashboard` documents **don't** necessarily need to be used with Shiny. You could use this framework to make a dashboard-style layout which does **not** include Shiny interactions such as input widgets (only other interactive components, such as Plotly or htmlwidgets).  
If so, it can be knitted into a standalone document which doesn't need a connection to a running R instance. You could just post it to your own website, for example, without running an R server continuously.

For our final project, you **will be** using Shiny anyway. In that case, there are a few other differences between the two options, including how you write up the code and how you control the layout. It seems that `shinydashboard` is best thought of as a very nice theme for Shiny dashboards, while `flexdashboard` can be used more generally but might not always integrate with Shiny quite as well.

+ [https://shiny.rstudio.com/articles/dashboards.html]
+ [https://stackoverflow.com/questions/37992147/r-shiny-which-hammer-straight-shiny-flexdashboard-or-shinydashboard]

Please see examples online. As a team, you'll choose one of these options for the final project. Meanwhile, below is our basic app from before, rewritten in the `shinydashboard` framework.

## `shinydashboard` example

Using `shinydashboard`, we put each content type inside a `box` item so it can be moved flexibly around the `dashboardBody`. If we made several tabs/pages, we could navigate them using the `dashboardSidebar`.

```{r shinydashboard, warning=FALSE, message=FALSE}
library(shinydashboard)
shinyApp(
  
  ui = dashboardPage(
    dashboardHeader(title = "ShinyDashboard Layout Example"),
    
    dashboardSidebar(),
    
    dashboardBody(
      fluidRow(
        box(
          title = "Controls",
          sliderInput("point_size", label = "Point size:",
                      min = 0.5, max = 3, value = 2, step = 0.5),
          checkboxInput("show_conf", label = "Include confidence band")
        ),
        
        box(
          title = "Results",
          textOutput("is_conf_shown"), 
          plotOutput("state_plot")

        )
      )
    )
  ),
  
  server = function(input, output) {
    output$state_plot <- renderPlot({
      
      ggplot(state_df, aes(x = HS.Grad, y = Illiteracy)) +
        geom_point(size = input$point_size) + 
        geom_smooth(method = "lm", se = input$show_conf) +
        labs(x = "HS Graduation Rate",
             title = "Education vs Illiteracy in US States in 1977")
      
    })
    
    output$is_conf_shown <- renderText({
      if(input$show_conf) {
        return("Regression line with 95% confidence band:")
      } else {
        return("Regression line (no confidence band):")
      }
    })
  },
  
  options = list(height = 650)
)
```



## `flexdashboard` example

This can't be embedded inside our current RMarkdown document; we would need to specify in the file header that it will be a `flexdashboard` document type. Instead, see the example in `Lecture18b_FlexDashboard.Rmd`, based on RStudio's example here:

* [https://rmarkdown.rstudio.com/flexdashboard/shiny.html]

***

# Hosting on [ShinyApps.io](https://www.shinyapps.io/)

To make a Shiny app which is **not** inside a RMarkdown document, the code structure may be slightly different than what we've seen in class. However, there are plenty of examples online that you can mimic to get started.

Finally, you will need to host your class projects online at [ShinyApps.io](https://www.shinyapps.io/), as you did in Lab 10.

For example, [here is a final project from a previous semester](https://hlandis.shinyapps.io/interactive_graphics_group_project_05-09_version/), while [here is a Shiny app that Jerzy made for a client](https://civilstat.shinyapps.io/DarekRadioTiles).

In case you need to review the instructions for how to create a free ShinyApps.io account and deploy your Shiny apps there:

+ [https://shiny.rstudio.com/articles/shinyapps.html]
+ [http://docs.rstudio.com/shinyapps.io/]

